\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Experimental wordsmithing

In this work, we compare and contrast three modern solutions, the Extended Kalman Filter (EKF), the Sliding Window Filter (SWF), and a hybrid solution, the Multi-State Constraint Kalman Filter (MSCKF), that combines the strengths of both.
We present an experimental comparison of the SWF and MSCKF using a dataset consisting of IMU and camera data with accurate ground truth for both sensor motion and landmark positions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MULTI-STATE CONSTRAINT KALMAN FILTER} \label{sec:MSCKF}
The Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2007:ICRA} can be thought of as a hybrid of EKF-SLAM and the SWF.
The key idea of the MSCKF is to maintain a sliding window of vehicle poses and to simultaneously update each pose in the window using batch-optimized estimates of features that are visible across the entire window.
This update step typically occurs when a tracked feature goes out of view of the camera, but it may also be triggered if the number of vehicle states in the window exceeds some preset threshold.

@@

@@

@@

\subsection{Experiment 3: Effect of feature density}
Finally, we investigated the effect of feature density on the performance of both the MSCKF and SWF.
For this experiment, we modified the ``Starry Night'' dataset by creating synthetic feature distributions with larger spatial extents and more features than the original dataset.
We retained the original IMU data, but simulated camera measurements with lower measurement noise.
Figure \ref{fig:trajectory_groundtruth_100lessnoisy} shows the feature distribution for the 100-feature synthetic dataset.

@@

@@

    \caption{Comparison of cumulative Root Mean Squared Error (RMSE) of MSCKF, SWF, and IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (40, 60 or 100).}
    \label{fig:comp_3}
\end{figure}

>>>>

In this work, we compare and contrast three modern solutions, the Extended Kalman Filter (EKF), the Sliding Window Filter (SWF), and a hybrid solution, the Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA}, that combines the strengths of both.
We present an experimental comparison of the SWF and MSCKF using a dataset consisting of IMU and camera data with accurate ground truth for both sensor motion and landmark positions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MULTI-STATE CONSTRAINT KALMAN FILTER} \label{sec:MSCKF}
The Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA} can be thought of as a hybrid of EKF-SLAM and the SWF.
The key idea of the MSCKF is to maintain a sliding window of vehicle poses and to simultaneously update each pose in the window using batch-optimized estimates of features that are visible across the entire window.
This update step typically occurs when a tracked feature goes out of view of the camera, but it may also be triggered if the number of vehicle states in the window exceeds some preset threshold.

@@

Figure \ref{fig:comp_1} shows absolute translational and rotational errors for pure IMU integration and various parameter settings for the MSCKF and SWF.
For the MSCKF, we varied both the maximum number of observations before triggering an update and the minimum number of observations for a feature track to be used in an update.
For the SWF, we varied the number of states in the sliding window.
These parameters did not significantly affect the accuracy of either filter, however Figure \ref{fig:comp_1} shows some small gains in accuracy for larger feature track lengths and window sizes.

On this interval, the SWF slightly outperforms the MSCKF in terms of translational accuracy in the $y$- and $z$-directions, and significantly outperforms the MSCKF in terms of rotational accuracy about the $x$- and $y$-axes.
The MSCKF does not perform much better than pure IMU integration on this interval, likely due to the overall low number of feature tracks in this dataset.

@@

Figure \ref{fig:comp_2} shows absolute translational and rotational errors for pure IMU integration and the same MSCKF and SWF parameter settings as in Experiment 1.
Compared to Interval 1, the difference in performance between the MSCKF and SWF is less pronounced, with the exception of the SWF's clearly superior translational accuracy in the $y$-direction.
Neither filter performs substantially better than pure IMU integration on this interval, again likely due to the overall low number of feature tracks in this dataset.

@@

\subsection{Experiment 3: Effect of feature density}
In order to investigate the effect of feature density on the performance of the MSCKF and SWF, we modified the ``Starry Night'' dataset by creating synthetic feature distributions with larger spatial extents and more features than the original dataset.
We constructed each dataset so that the larger maps contained the same features as the smaller maps, plus additional features to make up the difference.
Although the camera measurements in these datasets are synthetic, the IMU data are unchanged from the original dataset.
Figure \ref{fig:trajectory_groundtruth_100lessnoisy} shows the feature distribution for the 100-feature synthetic dataset.
By generating longer feature tracks and increasing the number of features visible at each time step, these synthetic datasets allowed for a clearer comparison between the MSCKF and SWF.

@@

Figure \ref{fig:comp_3} compares translational and rotational root mean squared error (RMSE) of the MSCKF, SWF, and pure IMU integration on three synthetic datasets with 40, 60, and 100 features.
On all three datasets, the SWF outperforms the MSCKF by a wide margin, although the MSCKF's performance improves as more features are added.

@@

    \caption{Comparison of root mean squared error (RMSE) of the MSCKF, SWF, and pure IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (40, 60 or 100).}
    \label{fig:comp_3}
\end{figure}
